{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-06 Notebook LaTEX/Proposal/main.tex
>w<, changes

                x \in \RR \left | \; 

@@

        The parts coming will introduce the algorithms, explain key innovations behind the algorithm, and key variants of the algorithm. 
        The section at the end will give future works and extensions of the Catalyst framework. 

@@

@@

        This algorithm is often referred to as the inner loop. 
        The outer loop controls where the proximal point $y_{k}$ is evaluated at and computes Nesterov's momentum extrapolations. 

@@

        The error sequence $(\epsilon_k)_{k \ge 0}$ depends on the properties of the objective function. 
        For example, when $F$ has $\mu = 0$, 
            Lin's paper, Theorem 3.3
        {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = (\sqrt{5} - 1)/2$, and 
            \epsilon_k = \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}}, 
        \end{align}\label{eqn:catalyst-error-seq-cnvx}

@@

        This makes the iteration complexity of just the outer loop optimal. 
        In addition, to achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 

@@

        Take note that, the error sequence has $F^*$ the optimal value in both cases. 

@@

@@

        The following parts will complement the report and describe ideas on for choosing the termination criteria of the inner loop to evaluate $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$ which is the focus of his second paper on Catalyst Acceleration \cite{lin_catalyst_2018}. 
        To elucidate the matters consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ is $\mu + \kappa$ strongly convex, and therefore it admits the Polyak error bound condition: 

@@

        By choosing $x$ such that $\dist(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
        Unfortunately in practice, this is not used because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice. 

@@

@@

            \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in a error sequence without $F^*$, and simplier proof without using the Nesterov's estimating sequence. 
            \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth compositie objective. 

@@

>>>>

                x \in \RR^n \left | \; 

@@

        The parts coming will introduce the algorithms, explain its key innovations. 
        The last section reviews recent literatures on the topics and gives potential future works. 

@@

        With a fixed regularization parameter $\kappa > 0$, The outer loop (Definition \ref{def:lin-catalyst-original}) produces $(y_{k}, x_k)_{k \ge k}$ denote it by $\mathbb A$. 

@@

        We refer this algorithm as the inner loop and denote it by $\mathbb M$. 
        Without loss of generality assume it generates some convergence sequence $(z_{k, t})_{t \ge 0}$ where $k$ is the corresponding iteration counter of the outer loop. 

@@

        The choice of error sequence $(\epsilon_k)_{k \ge 0}$ determines iteration $\mathbb A, \mathbb M$. 
        The total iteration complexity of the algorithm counts the total number of inner loop iteration. 
        The term ``iteration complexity'' refers to the number of iterations required to achieve a desired accuracy, a concept related to the convergence rate of the algorithm. 
        The term ``complexity'' refers to the total number of oracle calls, in our context it depends on the specific implementation of $\mathbb M$. 
        Due to the fact that function $F$ is convex, we focus on the convergence rate of the optimality gap $F(x_k) - F^*\*$ for $\mathbb A$ and convergence of the model function $\mathcal M_F^{\kappa^{-1}}(\cdot, y_{k - 1})$ for $\mathbb M$ given $y_{k - 1}, \epsilon_k$ and initial guess $z_{k, 0}$. 
                \item State outer loop iteration complexity given error sequence for 
                    \item Strongly convex objective,
                    \item Non-strongly but strongly convex objective. 
                \item State the linear convergence rate assumption of the inner function. 
                \item State the iteration complexity of the inner loop given the specific error sequence.

            \end{enumerate}
        }
        \par
        \subsubsection{Outer loop iteration complexity}
            The error sequence $(\epsilon_k)_{k \ge 0}$ governs the convergence rate of the outer loop for $F(x_k) - F^*$ to converge. 
            Depending on either $\mu > 0$, or $\mu = 0$, the choice of $(\epsilon_k)_{k\ge 0}$ differs. 
            The theorem that follows state the error sequence required for the outer loop to retain optimal convergence rate, they are Theorem 3.3, 3.1 in Lin et al. \cite{lin_universal_2015}. 
            \begin{theorem}[Outer loop convergence strongly convex]

            \end{theorem}
            \begin{theorem}[Outer loop convergence convex but not strongly convex]

            \end{theorem}
            For example, when $F$ has $\mu = 0$, 
            \todo{
                Lin's paper, Theorem 3.3
            }
            {\hl{Lin }}\cite[Theorem 3.3]{lin_universal_2015} suggested $\alpha_0 = \left(\sqrt{5} - 1\right)/2$, and 
            \begin{align}
                \epsilon_k = \frac{2(F(x_0) - F^*)}{9(k + 2)^{4 + \eta}}, 
            \end{align}\label{eqn:catalyst-error-seq-cnvx}

@@

            In this scenario, the iteration complexity of the outer loop optimal. 
            To achieve optimal convergence for the outer loop when $\mu > 0$ for $F$, 

@@

            Take note that, the error sequence requires knowledge on $F^*$. 

@@

        \subsubsection{Inner loop complexity}
            The following parts will complement the report and talk about the convergence of the inner loop, and the overall algorithm. 

@@

            Denote the outer loop algorithm by $\mathbb A$, and the inner loop algorithm by $\mathbb M$. 
            The outer loop iteration algorithm generates $(x_k, y_k)_{k \ge0}$ by Definition \ref{def:lin-catalyst-original} and, for genericity assume that the inner loop is an iterative generating $(z_{k, i})_{i \ge 0}$ where $k$ denotes the iteration index of the outer loop. 
            Lemma B1, B2 and Appendix item B.4 from Lin et al. \cite{lin_universal_2015} shows the convergence of the inner loop. 
            It requires an error sequence $(\epsilon_k)_{k \ge 0}$ given in prior to assert the convergence rate of the outer loop. 
            With warm starting, it uses the most recent iterate $x_{k - 1}$ (or equivalently some extrapolation using the most recent iterates) to initialize the inner loop to find the next $x_k \in \mathcal J_{F, \kappa^{-1}}^{\epsilon_{k}} y_{k - 1}$.
            Warm starting the inner loop couples its convergence rate with the outer loop, allowing for the overall complexity analysis.  
            Given the error sequence in Equation \ref{eqn:catalyst-error-seq-s-cnvx}, if $\mu > 0$ so the outer loop has linear convergence on $F(x_k) - F^*$, then it demands a linear convergence rate on model function $\mathcal M^{\kappa^{-1}}_F(\cdot, y_{k - 1})$ for the inner loop to an optimal complexity overall. 
            If $\mu = 0$, and $(\epsilon_k)_{k \ge0}$ is given by Equation \ref{eqn:catalyst-error-seq-cnvx}, so the outer loop has $\mathcal O(1/k^2)$ convergence rate on $F(x_k) - F^*$. 
            With the assumption $\argmin_x F(x)$ is a bounded set and the inner loop converges linearly, an optimal overall complexity is achievable. 
            Lin et al.'s second paper on Catalyst Acceleration \cite{lin_catalyst_2018} describes new ideas to choose the termination criteria for the inner for evaluating $\mathcal J_{\kappa^{-1}F}^{\epsilon_k} y_k$. 
            To elucidate, consider the model function $\mathcal M_F^{\kappa^{-1}}(x; y)$ to be $\mu + \kappa$ strongly convex. 
            Therefore, it has error bound condition: 

@@

            By choosing $x$ such that $\dist\left(\mathbf 0, \partial \mathcal M_F^{1/\kappa}(x; y)\right) \le \epsilon$, it ensures $x \in \mathcal J^\epsilon_{\kappa^{-1}F}(y)$. 
            Unfortunately in practice, this is a difficult strategy because a full gradient evaluation on the model function $\mathcal M^{1/\kappa}_F(\cdot; y)$ is costly (compare to the small amount required for VRM, which is just the gradient of a few samples.), so Lin suggested alternatives of inner loop termination criteria, and/or upper bounds of inner loop iteration to make Catalyst Acceleration competitive in practice. 

@@

                    \item [$\square$] The assumption of bounded level set to show the convergence when objective is not strongly convex. 

@@

                \item A relative termination criteria that bounds the gradient of the problem in the inner loop, which results in an error sequence without $F^*$, and simpler proof without using the Nesterov's estimating sequence. 
                \item A more comprehensive convergence proof, for 2 different type of error bounds with, including the smooth plus nonsmooth composite objective. 

@@

            The list above is not exhaustive.
